Supporting information for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-12-15 Documents/supporting_information.tex
More changes for PNAS.

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{geometry}

\usepackage{amsmath}
\usepackage{graphics}
\usepackage{tikz}

@@

% Tweak captions.
\usepackage[font=sf,
            labelfont=bf,
            labelsep=period,
            singlelinecheck=off]{caption}

% Make float text and math sans serif.
\usepackage[font=sf]{floatrow}
\usepackage{sansmath}
\usepackage{etoolbox}
\AtBeginEnvironment{table}{\sansmath}
\AtBeginEnvironment{figure}{\sansmath}
\floatsetup[table]{capposition=top,  % Table captions on top.
                   justification=justified}  % Don't center by default.

@@

\usepackage[pdfborder={0 0 0}]{hyperref}

@@

\title{Supporting Information for\\
  \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127
    countries}}

\author[a,1]{Jan Medlock}
\affil[a]{Department of Biomedical Sciences,
  Oregon State University,
  106 Dryden Hall,
  Corvallis, OR 97331-4801,
  USA}
\author[b]{Abhishek Pandey}
\author[b]{Alyssa S.~Parpia}
\author[b]{Amber Tang}
\author[b]{Laura A.~Skrip}
\author[b]{Alison P.~Galvani}
\affil[b]{Center for Infectious Disease Modeling and Analysis,
  Yale School of Public Health,
  135 College Street,
  New Haven, CT 06510-2483,
  USA}
\affil[1]{To whom correspondence should be addressed.
  Email: \href{mailto:jan.medlock@oregonstate.edu}
  {\texttt{jan.medlock@oregonstate.edu}}.}

@@

\begin{figure}
  \begin{center}
    \includegraphics{../Codes/plots/transmission_rate.pdf}
  \end{center}
  \caption{Country-specific distributions of transmission rate,
    $\bar{\beta}$, calculated based on UNAIDS historical estimates of
    country prevalence and incidence.  See \autoref{model_fitting}.}
  \label{transmission_rate}
\end{figure}

@@

\begin{figure}
   \centering
   \includegraphics{../Codes/plots/prcc.pdf}
   \caption{Sensitivity of global HIV incidence from 2015 to 2035 to
     model parameters.  Left is the sensitivity of infections averted
     by 95--95--95, relative to status quo.  Right is the sensitivity
     of vaccination with status quo levels of diagnosis and treatment,
     relative to status quo.  Sensitivity is measured by the partial
     rank correlation coefficient (PRCC).}
   \label{PRCCs}
\end{figure}

@@

% \printbibliography
\bibliography{supporting_information}
\bibliographystyle{pnas2011}

>>>>

\usepackage{common}

\usepackage{geometry}

\usepackage{amsmath}
\usepackage{tikz}

@@

@@

@@

\title{Supporting information for\\
  \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127
    countries}}

\author[a,1]{Jan Medlock}
\affil[a]{Department of Biomedical Sciences,
  Oregon State University,
  106 Dryden Hall,
  Corvallis, OR 97331-4801}
\author[b]{Abhishek Pandey}
\author[b]{Alyssa S.~Parpia}
\author[b]{Amber Tang}
\author[b]{Laura A.~Skrip}
\author[b]{Alison P.~Galvani}
\affil[b]{Center for Infectious Disease Modeling and Analysis,
  Yale School of Public Health,
  135 College Street,
  New Haven, CT 06510-2483}
\affil[1]{To whom correspondence should be addressed.
  Email: \href{mailto:jan.medlock@oregonstate.edu}
  {\texttt{jan.medlock@oregonstate.edu}}.}

@@

\begin{figure}
  \begin{center}
    \input{../Codes/plots/transmission_rate.pgf}
  \end{center}
  \caption{Country-specific distributions of transmission rate,
    $\bar{\beta}$, calculated based on UNAIDS historical estimates of
    country prevalence and incidence.  See \autoref{model_fitting}.}
  \label{transmission_rate}
\end{figure}

@@

\begin{figure}
   \centering
   \input{../Codes/plots/prcc.pgf}
   \caption{Sensitivity of global HIV incidence from 2015 to 2035 to
     model parameters.  Left is the sensitivity of infections averted
     by 95--95--95, relative to status quo.  Right is the sensitivity
     of vaccination with status quo levels of diagnosis and treatment,
     relative to status quo.  Sensitivity is measured by the partial
     rank correlation coefficient (PRCC).}
   \label{PRCCs}
\end{figure}

@@

% \printbibliography
\bibliography{supporting_information}
\bibliographystyle{pnas-new}
